Specialisation in food webs scales with species richness but not with latitude

### 2017-09-03 manuscript/latitudepaper_submitted.tex
foundup of edited code files

\begin{figure}[h]
% \centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to species richness and the proportions of basal resources (\% Basal), intermediate 
consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were used as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

\begin{figure}[h]
% \centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
proportion was very similar to those of the scaling relationships with link density, except for the 
scaling of generality with the proportion of top predators where there was no effect of latitude on the 
size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}

>>>>

\begin{figure}[h]
\centerline{\includegraphics*[width=.85\textwidth]{Figures/by_TL/scaling_with_S/proportions/fitlines_nonts.eps}}
\caption{Scaling relationships for re-scaled link density, generality, and vulnerability 
relative to species richness and the proportions of basal resources (\% Basal), intermediate 
consumers (\% Intermediate), or top predators (\% Top) in a food web. Link density, generality,
and vulnerability were each re-scaled to remove the effects of latitude and ecosystem
type. As these relationships take the form of power laws, we did this by dividing the food-web
property (e.g. link density) by the predictor (e.g. \% Basal) raised to an exponent including the 
effects of latitude and, where applicable, ecosystem type and the interaction between ecosystem
type and latitude. Note that in all cases estuarine food webs were used as the baseline 
ecosystem type, but that at most two ecosystem types had interactions between ecosystem type and
latitude retained in the best-fit model (see \emph{results} for specifics). For each relationship, 
we show the re-scaled values (white circles) as well as the overall scaling relationship using estuarine
ecosystems as a baseline (black line, N=166 food webs). For a figure with the uncorrected values,
see Fig.~\emph{S1}, \emph{Appendix S4}.}
\label{props_v_lat}
\end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/justS_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with species richness across ecosystem
types and over latitude. We show the estimated scaling exponent for species richness (black
line) with its 95\% confidence interval (in grey), based on N=166 empirical food webs.
Latitude is given in degrees from the equator regardless of direction. The
behaviour of exponents for the scaling of generality and vulnerability with
species richness was very  similar to those for link density, except for the
scaling of generality in streams where  the size of the exponent increased
towards the poles. See Fig.~\emph{S2, Appendix 5} for  all scaling
relationships.} \label{S} \end{figure}

\begin{figure}[h]
\centerline{\includegraphics*[height=.65\textheight]{Figures/by_TL/marginal/BIT_marginal_latitude.eps}}
\caption{Changes to the scaling of link density with the proportions of basal resources, intermediate
consumers, or top predators in a food web across ecosystem types and over latitude. For each proportion
we show the estimated scaling exponent (black line) with its 95\% confidence interval (in grey), based
on N=166 empirical food webs. Latitude is given in degrees from the equator regardless of direction. 
The behaviour of exponents for the scaling relationships of generality and vulnerability with each 
proportion was very similar to those of the scaling relationships with link density, except for the 
scaling of generality with the proportion of top predators where there was no effect of latitude on the 
size of the exponent in any ecosystem type. See Figs.~\emph{S3-S5, Appendix 5} for all scaling relationships.}
\label{BIT}
\end{figure}
